---
title: "Course Project"
author: "Group D7"
output:html_document
---

 
Reading and Displaying Data
```{r}
df<-read.csv("C:/Users/cheta/Desktop/cleaned_reviews.csv")
head(df)
```

FINDING ROWS WITH NULL VALUES 

```{r}
rows_with_null<-df[apply(is.na(df),1,any),]
```

FINDING COLUMNS WITH ANY NULL VALUES
```{r}
cols_with_null<- df[apply(is.na(df),2,any)]
```

PRINTING THE ROWS AND COLUMN WITH NULL VALUES
```{r}
print(rows_with_null)
```

```{r}
print(cols_with_null)
```

Displaying Data Dimensions:-

```{r}
dim(df)
```


Displaying Data Structure:-It provides information about the data types of columns and other data-related details.

```{r}
str(df)
```

Summary of Data:-It includes statistics and information about the data in each column.
```{r}
summary(df)
```

Installing the "dplyr" Package:-It is commonly used for data manipulation and transformation.

```{r}
install.packages("dplyr")
```
Loading the "dplyr" Package
```{r}
library(dplyr)
```

Loading the "ggplot2" Package
```{r}
library(ggplot2)
```

Creating a Box Plot

Creating  a box plot that visualizes the distribution of review scores by sentiment.
```{r}
boxplot_plot <- ggplot(df, aes(x =sentiments, y =review_score)) +
  geom_boxplot() +
  labs(title = "Boxplot")
print(boxplot_plot)
```
Creating a Scatter Plot

Creating the Scatter plot to visualize the relationship between review scores and sentiments.
```{r}
library(ggplot2)
ggplot(data=df,mapping=aes(x=sentiments,y=review_score))+geom_point()

```

Creating a Grouped Box Plot

creates a grouped box plot using "ggplot2" to visualize the distribution of review scores by sentiment.

```{r}
library(ggplot2)
ggplot(data=df,mapping=aes(x=sentiments,y=review_score,fill=sentiments))+geom_boxplot()

```

Creating a Scatter Plot for Review Length and Sentiments

Creates a scatter plot to visualize the relationship between sentiments and the length of cleaned reviews.

```{r}
library(ggplot2)
ggplot(data=df,mapping=aes(x=sentiments,y=cleaned_review_length))+geom_point()

```


Calculating Percentage of Review Scores

Calculate the percentage of each unique value in the review_score column

```{r}
rating_counts <- table(df$review_score)
rating_pct <- (rating_counts / nrow(df)) * 100
print(rating_pct)
```

Analyzing Text Data

These code chunks focus on analyzing text data, including checking data types, converting text data to character type, checking for missing values, and creating a histogram to visualize word count distribution in the "cleaned_review" column.

```{r}
barplot(rating_pct, main = "Rating Percentages", xlab = "Rating", ylab = "Percentage", col = "blue")
```


To calculate words per review

check the datatype of the cleaned_review column
```{r}
class(df$cleaned_review)

```

convert the text column to character
```{r}
df$Text <- as.character(df$cleaned_review)
```

check the missing value
```{r}
sum(is.na(df$Text))

```


```{r}
library(ggplot2)
WordsPerReview <- sapply(strsplit(df$Text, ' '), length)
#create the histogram
ggplot(data = data.frame(WordsPerReview = WordsPerReview), aes(x = WordsPerReview)) +
  geom_histogram(bins = 100, fill = "blue", color = "black") +
  xlab("cleaned_review") +  
  theme_minimal()


```

Creating a New Dataframe

```{r}
new_df <- df[, c('cleaned_review', 'review_score')]
```

Renaming Column Names
```{r}
colnames(new_df) <- c('Rating', 'Review')
```

Creating Sentiment Mapping Function
```{r}
apply_sentiment <- function(Rating) {
  if (Rating <= 2) {
    return(0)
  } else {
    return(1)
  }
}

rating <- 3
sentiment <- apply_sentiment(rating)
print(sentiment)
```
Setting Warning Conflicts to FALSE
```{r}
options(warn.conflicts = FALSE)
```






Creating Review Score Visualizations

```{r}
library(ggplot2)
library(gridExtra)

# Calculate value counts for review scores
review_counts <- table(df$review_score)

# Create a count plot
count_plot <- ggplot(data = df, aes(x = review_score)) +
  geom_bar() +
  labs(title = "Review Score Count Plot")
print(count_plot)
```

Creating Review Score Visualizations
```{r}
# Load the necessary libraries
library(ggplot2)

# Sample data for review counts
review_counts <- data.frame(
  review_score = c("Excellent", "Very Good", "Good", "Fair", "Poor"),
  n = c(20, 30, 15, 10, 5)
)

# Create a pie chart
pie_chart <- ggplot(data = review_counts, aes(x = "", y = n, fill = review_score)) +
  geom_bar(stat = "identity") +
  coord_polar(theta = "y") +
  theme_void() +
  labs(title = "Review Score Distribution")

# Print the pie chart
print(pie_chart)


```


Text Mining and Sentiment Analysis
```{r}
install.packages("tm")
```


```{r}
install.packages("syuzhet")
```


```{r}
library(tm)
library(syuzhet)
```

Sample text data
```{r}
text_data <- c(
  "Its very nice product, i just loved it",
  "The customer service was terrible.",
  "The movie was just okay, nothing special.",
  "I hate this product.",
  "It was good but not that good",
  "This is the most excellent product I have used till",
  "The product is okay, does what it's supposed to do.", 
  "I'm disappointed with this product; it failed to meet my expectations.", 
  "This is the best product I've ever used!",
  "The product is middle-of-the-road, quite what you'd expect.", 
  "I'm overjoyed with the results; this is a premium quality product!",
  "Customer service was fine, nothing special but not bad either.", 
  "The quality is subpar, not what I was hoping for at all.",
  "I'm incredibly pleased with the customer service; they're fantastic!",
  "It's a standard service, meets expectations but doesn't exceed them.",
  "I regret this purchase; the product is not worth the money.", 
  "Absolutely love how this performs, it's perfect for my needs.",
  "This service has been a game-changer, so grateful I found it!", 
  "I'm thrilled with the results, it's just what I was looking for!", 
  "It's an average item, not bad for the price.", 
  "The quality of this item is outstanding, exceeded my expectations!",
  "I'm delighted with my purchase, would buy it again in a heartbeat!",
  "Service was competent, though it lacked that extra touch.",
  "This has to be the greatest invention, it makes life so much easier!",
  "The product works as intended but doesn't stand out in any way.", 
  "Customer service was unhelpful and frustrating to deal with.", 
  "This item is fairly ordinary, neither good nor bad.",
  "It's an adequate product, though there's room for improvement.",
  "This item is poorly made and started falling apart quickly.",
  "I'm not satisfied with the service; it was a waste of time.",
  "The product is far below the quality advertised.",
  "It's a standard service, meets expectations but doesn't exceed them.",
  "I had a bad experience with this service; I wouldn't recommend it.",
  "This has been a letdown; the item does not perform as promised.",
  "I'm unhappy with the purchase; it's not up to the standard.",
  "The item is acceptable, but I might try something different next time.",
  "I love this product",
  "This is terrible",
  "It's okay"
  
)
```




Create a data frame with the text data
```{r}
df <- data.frame(Text = text_data)
```


Preprocess the text data using the tm package (same as in the previous example)
Perform sentiment analysis using the syuzhet package.
```{r}
sentiments <- get_sentiment(df$Text, method = "afinn")
```


Combine the results with the original data frame
```{r}
df <- cbind(df, Sentiment = sentiments)
```


Print the results
```{r}
print(df)
```

```{r}
df_sorted_ascending <- df[order(df$Sentiment), ]

df_sorted_ascending
```
